### 2025-04-19 evaluating-prediction-accuracy.qmd
20250419 - calibration plots

```{r}
library("petersenlab")
library("tidyverse")
library("pROC")
library("magrittr")
library("viridis")
```

@@

>>>>

```{r}
library("petersenlab")
library("tidyverse")
library("pROC")
library("magrittr")
library("viridis")
library("viridisLite")
library("msir")
```

### Load Data {#sec-predictionAccuracyLoadData}

```{r}
#| eval: false
#| include: false

load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/player_stats_seasonal.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/players_projections_weekly.RData", fsep = ""))
load(file = file.path(path, "/OneDrive - University of Iowa/Teaching/Courses/Fantasy Football/Data/players_projections_seasonal.RData", fsep = ""))
```

```{r}
load(file = "./data/player_stats_weekly.RData")
load(file = "./data/player_stats_seasonal.RData")
load(file = "./data/players_projections_weekly.RData")
load(file = "./data/players_projections_seasonal.RData")
```

@@

## Accuracy of Fantasy Projections {#sec-accuracyProjections}

### Seasonal Projections {#sec-accuracyProjectionsSeasonal}

To evaluate the accuracy of projections, we must first merge projections with actual performance.

```{r}
player_stats_seasonal_subset <- player_stats_seasonal %>% 
  filter(!is.na(player_id))

nfl_playerIDs_subset <- nfl_playerIDs %>% 
  filter(!is.na(gsis_id)) %>% 
  distinct(gsis_id, .keep_all = TRUE) %>% # keep only rows that do not have duplicate values of gsis_id
  select(-all_of(c("team", "position", "height", "weight", "age")))

players_projectedPoints_seasonal_combined$season <- as.integer(players_projectedPoints_seasonal_combined$season)

player_stats_seasonal_subset_IDs <- left_join(
  player_stats_seasonal_subset,
  nfl_playerIDs_subset,
  by = c("player_id" = "gsis_id")
) %>% 
  filter(!is.na(mfl_id))

projectionsWithActuals_seasonal <- full_join(
  player_stats_seasonal_subset_IDs,
  players_projectedPoints_seasonal_combined,
  by = c("mfl_id" = "id", "season"),
  suffix = c("", "_proj"),
)

projectionsWithActuals_seasonal <- projectionsWithActuals_seasonal %>% 
  unite(
    "player_id_season",
    player_id,
    season,
    remove = FALSE
  )

playersWithHighProjectedOrActualPoints <- projectionsWithActuals_seasonal %>% 
  filter(raw_points > 100 | fantasyPoints > 100) %>% 
  select(player_id_season) %>% 
  pull()

projectionsWithActuals_seasonal_qb <- projectionsWithActuals_seasonal %>% 
  filter(position_group == "QB")

projectionsWithActuals_seasonal_rb <- projectionsWithActuals_seasonal %>% 
  filter(position_group == "RB")

projectionsWithActuals_seasonal_wr <- projectionsWithActuals_seasonal %>% 
  filter(position_group == "WR")

projectionsWithActuals_seasonal_te <- projectionsWithActuals_seasonal %>% 
  filter(position_group == "TE")

projectionsWithActuals_seasonal_k <- projectionsWithActuals_seasonal %>% 
  filter(position == "K")

projectionsWithActuals_seasonal_dl <- projectionsWithActuals_seasonal %>% 
  filter(position_group == "DL")

projectionsWithActuals_seasonal_lb <- projectionsWithActuals_seasonal %>% 
  filter(position_group == "LB")

projectionsWithActuals_seasonal_db <- projectionsWithActuals_seasonal %>% 
  filter(position_group == "DB")
```

```{r}
player_stats_seasonal_subset_IDs %>% 
  filter(!is.na(gsis_id)) %>% 
  group_by(gsis_id) %>% 
  filter(n() > 1) %>% 
  head()
```

#### Overall {#sec-accuracyProjectionsSeasonalOverall}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal$raw_points,
  actual = projectionsWithActuals_seasonal$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalOverall
#| fig-cap: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_seasonal$raw_points,
  y = projectionsWithActuals_seasonal$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

calibrationLoessPredictionInterval <- data.frame(
  x = calibrationLoessModel$x,
  y = calibrationLoessModel$y,
  lower = calibrationLoessModel$lower,
  upper = calibrationLoessModel$upper)

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal$raw_points,
  projectionsWithActuals_seasonal$fantasyPoints), na.rm = TRUE) + 50

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

#### Quarterbacks {#sec-accuracyProjectionsSeasonalQB}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_qb$raw_points,
  actual = projectionsWithActuals_seasonal_qb$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_seasonal_qb$raw_points,
  y = projectionsWithActuals_seasonal_qb$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

calibrationLoessPredictionInterval <- data.frame(
  x = calibrationLoessModel$x,
  y = calibrationLoessModel$y,
  lower = calibrationLoessModel$lower,
  upper = calibrationLoessModel$upper)

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_qb$raw_points,
  projectionsWithActuals_seasonal_qb$fantasyPoints), na.rm = TRUE) + 50

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_qb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Quarterbacks"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_qb$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_qb$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

#### Running Backs {#sec-accuracyProjectionsSeasonalRB}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_rb$raw_points,
  actual = projectionsWithActuals_seasonal_rb$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_seasonal_rb$raw_points,
  y = projectionsWithActuals_seasonal_rb$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

calibrationLoessPredictionInterval <- data.frame(
  x = calibrationLoessModel$x,
  y = calibrationLoessModel$y,
  lower = calibrationLoessModel$lower,
  upper = calibrationLoessModel$upper)

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_rb$raw_points,
  projectionsWithActuals_seasonal_rb$fantasyPoints), na.rm = TRUE) + 0

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_rb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Running Backs"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_rb$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_rb$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

#### Wide Receivers {#sec-accuracyProjectionsSeasonalWR}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_wr$raw_points,
  actual = projectionsWithActuals_seasonal_wr$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalWRs
#| fig-cap: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_seasonal_wr$raw_points,
  y = projectionsWithActuals_seasonal_wr$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

calibrationLoessPredictionInterval <- data.frame(
  x = calibrationLoessModel$x,
  y = calibrationLoessModel$y,
  lower = calibrationLoessModel$lower,
  upper = calibrationLoessModel$upper)

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_wr$raw_points,
  projectionsWithActuals_seasonal_wr$fantasyPoints), na.rm = TRUE) + 40

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_wr,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Wide Receivers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_wr$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_wr$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

#### Tight Ends {#sec-accuracyProjectionsSeasonalTE}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_te$raw_points,
  actual = projectionsWithActuals_seasonal_te$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalTEs
#| fig-cap: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_seasonal_te$raw_points,
  y = projectionsWithActuals_seasonal_te$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

calibrationLoessPredictionInterval <- data.frame(
  x = calibrationLoessModel$x,
  y = calibrationLoessModel$y,
  lower = calibrationLoessModel$lower,
  upper = calibrationLoessModel$upper)

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_te$raw_points,
  projectionsWithActuals_seasonal_te$fantasyPoints), na.rm = TRUE) + 0

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_te,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Tight Ends"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_te$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_te$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

#### Kickers {#sec-accuracyProjectionsSeasonalK}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_k$raw_points,
  actual = projectionsWithActuals_seasonal_k$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalKs
#| fig-cap: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_seasonal_k$raw_points,
  y = projectionsWithActuals_seasonal_k$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

calibrationLoessPredictionInterval <- data.frame(
  x = calibrationLoessModel$x,
  y = calibrationLoessModel$y,
  lower = calibrationLoessModel$lower,
  upper = calibrationLoessModel$upper)

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_k$raw_points,
  projectionsWithActuals_seasonal_k$fantasyPoints), na.rm = TRUE) + 100

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_k,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Kickers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_k$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_k$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

#### Defensive Linemen {#sec-accuracyProjectionsSeasonalDL}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_dl$raw_points,
  actual = projectionsWithActuals_seasonal_dl$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalDLs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_seasonal_dl$raw_points,
  y = projectionsWithActuals_seasonal_dl$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

calibrationLoessPredictionInterval <- data.frame(
  x = calibrationLoessModel$x,
  y = calibrationLoessModel$y,
  lower = calibrationLoessModel$lower,
  upper = calibrationLoessModel$upper)

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_dl$raw_points,
  projectionsWithActuals_seasonal_dl$fantasyPoints), na.rm = TRUE) + 0

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_dl,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Defensive Linemen"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_dl$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_dl$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

#### Linebackers {#sec-accuracyProjectionsSeasonalDL}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_lb$raw_points,
  actual = projectionsWithActuals_seasonal_lb$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalLBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_seasonal_lb$raw_points,
  y = projectionsWithActuals_seasonal_lb$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

calibrationLoessPredictionInterval <- data.frame(
  x = calibrationLoessModel$x,
  y = calibrationLoessModel$y,
  lower = calibrationLoessModel$lower,
  upper = calibrationLoessModel$upper)

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_lb$raw_points,
  projectionsWithActuals_seasonal_lb$fantasyPoints), na.rm = TRUE) + 0

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_lb,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Linebackers"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_lb$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_lb$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

#### Defensive Backs {#sec-accuracyProjectionsSeasonalDB}

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_db$raw_points,
  actual = projectionsWithActuals_seasonal_db$fantasyPoints,
  dropUndefined = TRUE
)
```

```{r}
#| label: fig-calibrationPlotSeasonalDBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

#95 prediction interval based on LOESS model
calibrationLoessModel <- msir::loess.sd(
  x = projectionsWithActuals_seasonal_db$raw_points,
  y = projectionsWithActuals_seasonal_db$fantasyPoints,
  nsigma = qnorm(.975),
  na.action = "na.exclude")

calibrationLoessPredictionInterval <- data.frame(
  x = calibrationLoessModel$x,
  y = calibrationLoessModel$y,
  lower = calibrationLoessModel$lower,
  upper = calibrationLoessModel$upper)

plotRangeMax <- max(c(
  projectionsWithActuals_seasonal_db$raw_points,
  projectionsWithActuals_seasonal_db$fantasyPoints), na.rm = TRUE) + 0

ggplot2::ggplot(
  data = projectionsWithActuals_seasonal_db,
  aes(
    x = raw_points,
    y = fantasyPoints)) + 
  coord_cartesian(
    xlim = c(0, plotRangeMax),
    ylim = c(0, plotRangeMax),
    expand = FALSE) +
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = lower),
    color = "red",
    linetype = "dashed") + #Lower estimate of 95% prediction interval of linear model
  geom_line(
    data = calibrationLoessPredictionInterval,
    aes(
      x = x,
      y = upper),
    color = "red",
    linetype = "dashed") + #Upper estimate of 95% prediction interval of linear model
  geom_smooth(
    method = "loess",
    color = viridisLite::viridis(3)[3],
    fill = viridisLite::viridis(3)[1],
    alpha = 0.7) + #95% confidence interval of LOESS model
  geom_abline(
    slope = 1,
    intercept = 0) +
  labs(
    x = "Projected Fantasy Points",
    y = "Actual Fantasy Points",
    title = "Calibration Plot for Seasonal Projections of Defensive Backs"
  ) +
  theme_classic() + 
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5)) # horizontal y-axis title
```

```{r}
petersenlab::accuracyOverall(
  predicted = projectionsWithActuals_seasonal_db$raw_points[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  actual = projectionsWithActuals_seasonal_db$fantasyPoints[which(projectionsWithActuals_seasonal$player_id_season %in% playersWithHighProjectedOrActualPoints)],
  dropUndefined = TRUE
)
```

### Weekly Projections {#sec-accuracyProjectionsWeekly}

To evaluate the accuracy of projections, we must first merge projections with actual performance.

```{r}

```
